\vskip-0.6in \Large Political Uncertainty

### 2015-03-25 GS-extension.tex
solve for b(j) in vote buyer B's FOC
add plus/minus and intuition for two roots on B's FOC

>>>>

								\item Rearranging to solve for $b(j)$:
							  		e^{- \frac{\left(\frac{\alpha + a(j) - b(j)}{\beta} - j\right)^2}{2\sigma_j^2} }= \frac{\beta\sigma_j \sqrt{2\pi}}{W_B} 
							  		- \left(\frac{\alpha + a(j) - b(j)}{\beta} - j\right)^2 =2\sigma_j^2 \ln\left(\frac{\beta\sigma_j \sqrt{2\pi}}{W_B} \right)
								Since the log statement on the RHS will almost certainly be negative, I can take the negative sign to the right and take the square root without worrying about imaginary numbers
							  		\frac{\alpha + a(j) - b(j)}{\beta} - j = \pm \sqrt{-2\sigma_j^2 \ln\left(\frac{\beta\sigma_j \sqrt{2\pi}}{W_B} \right)}
											\item Notice there are two roots: could be to the left of the mode (less than 0.5 cumulative probability), or to the right (more than 0.5 cumulative probability)
							  		\alpha + a(j) - b(j) = \pm \beta\sigma_j \sqrt{-2 \ln\left(\frac{\beta\sigma_j \sqrt{2\pi}}{W_B} \right)} + j \beta
							  		b(j) = \alpha + a(j)  - j \beta \pm \beta\sigma_j \sqrt{-2 \ln\left(\frac{\beta\sigma_j \sqrt{2\pi}}{W_B} \right)}
							  		b(j) = \alpha + a(j)  - \beta j \pm \beta\sigma_j \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}
								\item So, the bribe for legislator $j$ takes legislator j's preferences back to zero in expectation (the first three terms) and then relative to that, either adds or subtracts a term that involves WTP, variance and $\beta$
										\item Do we have a way of distinguishing between the two? They have very different implications for the CDF, even though the same implications for the pdf
										\item It makes more intuitive sense that the bribe would be increasing in $W_B$ (WTP)
										\item Perhaps we derive the different implications and let the data speak
										\item All the comparative statics will come out with same magnitude, both signs
										\item SOC is obviously okay (essentially $-x e^{\frac{x^2}{2}}$)
